Matching Bullets

### 2015-11-24 imaging-paper.Rnw
added references for plotly and shiny

\section{Application}
We've implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny[ref], allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly[ref], allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is available in Figure \ref{fig:app}. The application is available at the url \url{http://erichare.shinyapps.io/x3prproto}.

>>>>

\section{Application}
We've implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny \cite{shiny}, allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly \cite{plotly}, allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is available in Figure \ref{fig:app}. The application is available at the url \url{http://erichare.shinyapps.io/x3prproto}.
